Proposition of a New Experiment to Better Understand the Relation Between Typicality and Prototypes

### 2022-06-23 paper.tex
Added limitation on FE

				The biggest problematic related to the first two methods presented, which are the rating and the ranking systems, is that it is not feasible to either rate or rank every example in the whole 
				dataset, since it must have many images. In fact, it is very likely that a subject that has to rate or rank many examples will be tired after a certain number of images, polluting the results of the survey.
				The possible solution to this problem, is to give the subjects a subset of images to rate or rank. In this way, the collected data are most likely more reliable than the ones collected on all the dataset, 
				so it is more accurate the final result. \\
				Regarding only the typicality rating system, there is another problem. As hinted in previously, there is the possibility that this procedure leads to biased data. That is true because the form 
				created to collect the data, presents an example of an object that the subjects may not have thought of, and presenting the image, it may be possible that the subject gives a biased answer since 
				the image could have influenced the subject's judgement. For example, let us assume that the category chosen for the experiments is ``bird''. If a person is presented and image of a swan, 
				or a duck, and is asked to rate its typicality, most likely will rate it in the higher part of the scale, while if asked to list a certain number of birds it is more likely that it is not 
				present than that it is present.\\
				Talking about the ranking system, also this method can present biased data, since also this method presents the images, even if the bias is probably lower than the one that could result with the ranking system. 
				The major problem, with this method, is that the researcher must also design an algorithm to infer the typicality values from the rankings. This is a very difficult algorithm to design, since the rankings must 
				find a mapping to a scale.\\
				The alternative possibility described, can result in a lower bias since no images influence the subject's judgments. Recalling the previous example, in fact, if the subject did not think of 
				ducks and swans in the category ``bird'', these examples will not appear on the list. Although this technique presents a lower bias, it results in a great difficulty in prototype construction.

			\subsubsection{Considerations on how to choose}
				In order to give the proper weight to both the pros and cons and decide which is the best, the best decision is asking for help to a psychologist or a neuroscientist so that both pros and cons of the two 
				methods have the right weight and it is easier to decide which one is more convenient.
				As alternative, it is possible to try both the methods and see which one gives better results. In this way, both the possibilities will be used and there is the possibility to see which one is better in 
				terms of performance.

@@

		\noindent While collecting the needed data with the survey, it is possible to begin the feature extraction procedure. There are various possibilities for this step, as shown in Section \ref{sec:bfe}, which is
		the section dedicated to feature extraction background. 
		It could be interesting to test both classical and machine learning methods, to measure which one is the most efficient. Since feature extraction has already been described in the paper, this section will 
		present a discussion about the results of the presented methods' results. The main difference between the classical and the machine learning feature extraction techniques is human interpretability. 
		In fact, for classical feature extraction techniques, humans have no difficulty in interpreting the result of the process. For example, in edge extraction, humans have no difficulty in recognizing if the 
		edge extracted is correct or not seeing the original image. For example, in Figure \ref{fig:1} no one has any problem to recognize that the figure on the right is the one that draws the edges of the figure on the left, 
		while in Figure \ref{fig:4} there is no clear correlation between the feature and what it means in the image itself.
		Moreover, classical and machine learning features can give different weights to different features. 
		In fact, classical methods rely mostly on features that humans consider important, on the basis of general experience about the world, but also based on the way our brain works. An empirical confirmation of this fact 
		can be that if a person asks to another person to describe, for example, a common kingfisher, the person that should describe the bird will, most likely, start describing the dimension, the shape, and only 
		later the colour. Machine learning techniques, on the other hand, could give a very high importance to the fact that the bird is mainly blue and red, if they have access to the colour information. Due to the fact that 
		the blue colour is not very present in nature, the blue and red couple of colours can be highly characteristic of the common kingfisher, even if humans give, unconsciously and innately, more importance to 
		shape-related features.	\\
		If the data collection method chosen is the one that asks people to list the objects of the category, the feature extraction can happen in two possible ways. The first way is to use the data collected for 
		typicality judgments and collect also images of the examples that appear in the results. After collecting enough images, the feature extraction process can proceed as described earlier and use either  
		classical or machine-learning-based feature extraction methods. Although this is a possibility, there could be an alternative. The alternative seems interesting because it can be adapted to rely only on features 
		that humans identify as important. To do so, the survey should include a question that asks the subjects to list all the characteristics that the objects of the given macro category have in common. In this case, 
		the features are not strictly extracted by the dataset, but are listed by the subjects that take part in the survey. By doing so, the experiment takes into account, in the prototype, only the features that 
		human have listed, so only the features that are considered important by humans themselves. Although it is theoretically possible, this procedure will result in numerous complication in prototype construction.

@@

			\begin{figure*}[!t]
				\centering
				\begin{subfigure}[!t]{0.48\linewidth}
					\centerline{\includegraphics[width=0.9\linewidth]{imgs/swallow_edges.jpg}}
				\end{subfigure}
				\begin{subfigure}[!t]{0.48\linewidth}
					\centerline{\includegraphics[height=0.4\textheight]{imgs/swallow_2_edges.jpg}}
				\end{subfigure}
				\caption{Edge extraction of different swifts}
				\label{fig:9}
			\end{figure*}

>>>>

				\noindent The biggest problematic related to the first two methods presented, which are the rating and the ranking systems, is that it is not feasible to either rate or rank every example in the whole 
				dataset, since it must have many images. In fact, it is very likely that a subject that has to rate or rank many examples will be tired after a certain number of images, polluting the results of the survey.
				The possible solution to this problem, is to give the subjects a subset of images to rate or rank. In this way, the collected data are most likely more reliable than the ones collected on all the dataset, 
				so it is more accurate the final result. \\
				Regarding only the typicality rating system, there is another problem. As hinted in previously, there is the possibility that this procedure leads to biased data. That is true because the form 
				created to collect the data, presents an example of an object that the subjects may not have thought of, and presenting the image, it may be possible that the subject gives a biased answer since 
				the image could have influenced the subject's judgement. For example, let us assume that the category chosen for the experiments is ``bird''. If a person is presented and image of a swan, 
				or a duck, and is asked to rate its typicality, most likely will rate it in the higher part of the scale, while if asked to list a certain number of birds it is more likely that it is not 
				present than that it is present.\\
				Talking about the ranking system, also this method can present biased data, since also this method presents the images, even if the bias is probably lower than the one that could result with the ranking system. 
				The major problem, with this method, is that the researcher must also design an algorithm to infer the typicality values from the rankings. This is a very difficult algorithm to design, since the rankings must 
				find a mapping to a scale.\\
				The alternative possibility described, can result in a lower bias since no images influence the subject's judgments. Recalling the previous example, in fact, if the subject did not think of 
				ducks and swans in the category ``bird'', these examples will not appear on the list. Although this technique presents a lower bias, it results in a great difficulty in prototype construction.

			\subsubsection{Considerations on how to choose}

				\noindent In order to give the proper weight to both the pros and cons and decide which is the best, the best decision is asking for help to a psychologist or a neuroscientist so that both pros and cons of the two 
				methods have the right weight and it is easier to decide which one is more convenient.
				As alternative, it is possible to try both the methods and see which one gives better results. In this way, both the possibilities will be used and there is the possibility to see which one is better in 
				terms of performance.

@@

		\noindent While collecting the needed data with the survey, it is possible to begin the feature extraction procedure. There are various possibilities for this step, as shown in Section \ref{sec:bfe}, which is
		the section dedicated to feature extraction background. 
		It could be interesting to test both classical and machine learning methods, to measure which one is the most efficient. Since feature extraction has already been described in the paper, this section will 
		present a discussion about the results of the presented methods' results.

		\subsection{Considerations on feature extraction}

			\noindent The main difference between the classical and the machine learning feature extraction techniques is human interpretability. 
			In fact, for classical feature extraction techniques, humans have no difficulty in interpreting the result of the process. For example, in edge extraction, humans have no difficulty in recognizing if the 
			edge extracted is correct or not seeing the original image. In fact, in Figure \ref{fig:1} no one has any problem to recognize that the figure on the right is the one that draws the edges of the figure on the left, 
			while in Figure \ref{fig:4} there is no clear correlation between the feature and what it means in the image itself.
			Moreover, classical and machine learning features can give different weights to different features. 
			In fact, classical methods rely mostly on features that humans consider important, on the basis of general experience about the world, but also based on the way our brain works. An empirical confirmation of this fact 
			can be that if a person asks to another person to describe, for example, a common kingfisher, the person that should describe the bird will, most likely, start describing the dimension, the shape, and only 
			later the colour. Machine learning techniques, on the other hand, could give a very high importance to the fact that the bird is mainly blue and red, if they have access to the colour information. Due to the fact that 
			the blue colour is not very present in nature, the blue and red couple of colours can be highly characteristic of the common kingfisher, even if humans give, unconsciously and innately, more importance to 
			shape-related features.	\\
			If the data collection method chosen is the one that asks people to list the objects of the category, the feature extraction can happen in two possible ways. The first way is to use the data collected for 
			typicality judgments and collect also images of the examples that appear in the results. After collecting enough images, the feature extraction process can proceed as described earlier and use either  
			classical or machine learning based feature extraction methods. Although this is a possibility, there could be an alternative. The alternative seems interesting because it can be adapted to rely only on features 
			that humans identify as important. To do so, the survey should include a question that asks the subjects to list all the characteristics that the objects of the given macro category have in common. In this case, 
			the features are not strictly extracted by the dataset, but are listed by the subjects that take part in the survey. By doing so, the experiment takes into account, in the prototype, only the features that 
			human have listed, so only the features that are considered important by humans themselves. Although it is theoretically possible, this procedure will result in numerous complication in prototype construction.

		\subsection{Limitations of feature extraction}

			\noindent Examining the proposed methodologies, there are some limitations that can be seen.\\
			Talking about classical feature extraction techniques, for example, the first question that comes to mind is if these processes lose a lot of informations. For example, the edge detection algorithm loses all 
			the informations about the colours. Since numerous methods exists and are finalized in extracting various informations from an image, there is the possibility to preprocess through different steps the 
			images and collect the highest number possible of informations and combine them when constructing the prototype. This can help overcome the problem of losing informations in the feature extraction process but 
			arises another problem. In fact, it is not clear how the features should be weighted when combined. \\
			About the machine learning feature extraction, the biggest limitation is human interpretability. In fact, there is still no way to clearly interpret the features extracted by a machine learning system, since 
			these are in form of arrays of numbers. \\
			The biggest limitations come with the alternative method. This method can have two possible approaches, and one of them is asking people to list a set of features and using them to build the prototype. This 
			method is a big limitation since, as will be explained later, it is not clear how these features should be used in prototype construction.

@@

			\begin{figure*}[!t]
				\centering
				\begin{subfigure}[!t]{0.48\linewidth}
					\centerline{\includegraphics[width=0.9\linewidth]{imgs/swallow_edges.jpg}}
				\end{subfigure}
				\begin{subfigure}[!t]{0.48\linewidth}
					\centerline{\includegraphics[width=0.4\linewidth]{imgs/swallow_2_edges.jpg}}
				\end{subfigure}
				\caption{Edge extraction of different swifts}
				\label{fig:9}
			\end{figure*}
